### 2016-03-04 paper.tex
Add reference to W2'(x) graph
Small fixes

\engtitle{On the modification of the multistage bidding model with continuous bids and asymmetric information}

@@

\engabstract{%
  This paper is concerned with the modification of the multistage bidding model with continuous bids.
  Bidding takes place between two players for one unit of a risky asset.
  Player 1 knows the real price of the asset while Player 2 only knows probabilities of high and low prices of the asset.
  At each stage of the bidding players make real valued bids.
  The higher bid wins, and one unit of the risky asset is transacted to the winning player.
  The price of the transaction is equal to a convex combination of bids with a coefficient chosen in advance.
  Optimal strategies and the value of the $n$-stage game are found.
}

@@

  Пусть теперь $p_1 = h(\alpha), \; \alpha \in [0, 1]$.
  Введем обозначения
  \[
    \alpha^- = \inf \left\{ x \;|\; h(x) = h(\alpha) \right\}, \quad
    \alpha^+ = \sup \left\{ x \;|\; h(x) = h(\alpha) \right\}.
  \]
  Из \eqref{eq:W:lowerBound:parameterized} находим
  \begin{multline}\label{eq:g:+-}
    \G[p_1][h] = W_{2,n}(x + 1 - \alpha^- - \alpha^+) \enskip - \\
    - \int_0^{\alpha^-} \left(-\Co p_1 - \Dco h(u)\right) \di u
    - \int_{\alpha^+}^1 \left(\Dco p_1 + \Co h(u)\right) \di u.
  \end{multline}
  Поскольку $W_{2,n}(\cdot)$ -- дифференцируемая вогнутая функция, верно неравенство
  \begin{multline*}
    W_{2,n}(x + 1 - 2\alpha) \leqslant W_{2,n}(x + 1 - \alpha^- - \alpha^+) \enskip +\\
    + W_{2,n}'(x + 1 - \alpha^- - \alpha^+) \left( [ \alpha^+ - \alpha ] + [ \alpha^- - \alpha ] \right).
  \end{multline*}
  Из леммы \ref{lemma:hu:props} при $u_1 = (\alpha^- + \alpha^+)/2,\: u_2 = \alpha$ следует, что
  \[
  W_{2,n}'(x + 1 - \alpha^- - \alpha^+) = W_{2,n}'(x + 1 - 2\alpha) = h(\alpha).
  \]
  Так как $h(u)$ постоянная на $[\alpha^-, \alpha^+]$ и $h(\alpha) = p_1$ имеем
  \begin{multline*}
    W_{2,n}(x + 1 - \alpha^- - \alpha^+) \geqslant W_{2,n}(x + 1 - 2\alpha) - \\
    - \int_\alpha^{\alpha^+} \left( \Dco p_1 + \Co h(u) \right) \di u
    + \int_{\alpha^-}^\alpha \left( \Co p_1 + \Dco h(u) \right) \di u.
  \end{multline*}
  Используя оценку на $W_{2,n}(x + 1 - \alpha^- - \alpha^+)$ в \eqref{eq:g:+-}, получаем
  \begin{multline*}
    \G[p_1][h] \geqslant W_{2,n}(x + 1 - 2\alpha)
    - \int_\alpha^1 \biggl( \Dco h(\alpha) + \Co h(u) \biggr) \di u \; + \\
    + \int_0^\alpha \biggl( \Co h(\alpha) + \Dco h(u) \biggr) \di u = \G[h(\alpha)][h] = \Psi(h).
  \end{multline*}
  Таким образом, требуемое неравенство имеет место при любом значении $p_1 \in [0, 1]$.
\end{proof}

@@

\begin{example}
  Найдем оптимальные $f$ и $Q$ в игре $G_2(P)$.
  Из \eqref{eq:W1'} получаем
  \begin{equation*}
    W_1(x) = \begin{cases}
      x, &\; x \leqslant 1,\\
      1/4 (-1 + 2x - x^2), &\; -1 < x < 1,\\
      0, &\; x \geqslant 1.
    \end{cases}
  \end{equation*}
  Отсюда по формуле \eqref{eq:W':recursive} находим
  \begin{equation*}
    W'_2(x) = \frac{1}{2} \left( W_1(x+1) - W_1(x-1) \right) = \begin{cases}
      1, &\; x < -2,\\
      (4 - 4x - x^2)/8, &\; -2 \leqslant x < 0,\\
      (x - 2)^2/8, &\; 0 \leqslant x < 2,\\
      0, &\; x \geqslant 2.
    \end{cases}
  \end{equation*}
  \begin{figure}[h!]
    \begin{center}
      \includegraphics[height=6cm]{w2.eps}
      \fcaption{Функция $W_2'(x)$}
      \label{fig:w2}
    \end{center}
  \end{figure}
  Пусть $1/2 \leqslant P \leqslant 1$.
  Тогда искомое $\lambda$ находится как решение уравнения $(4 - 4\lambda - \lambda^2)/8 = P$, т.е. $\lambda = -2 + 2\sqrt{2 - 2P}$.
  Отсюда получаем
  \begin{equation*}
    Q(u) = W'_1(\lambda + 1 - 2u) = \begin{cases}
      1 - \sqrt{2 - 2P} + u, &\; u < \sqrt{2 - 2P},\\
      1, &\; u \geqslant \sqrt{2 - 2P}.
    \end{cases}
  \end{equation*}
  Пусть $\Dco < \sqrt{2 - 2P}$.
  Тогда для $f$ имеет место следующая формула:
  \begin{equation*}
    f(u) = \begin{cases}
      1 - \sqrt{2 - 2P} + (2u + \Dco)/3, &\; u \leqslant \sqrt{2 - 2P},\\
      1 - \frac{(\sqrt{2 - 2P} - \Dco)^3}{3(u - \Dco)^2}, &\; u > \sqrt{2 - 2P}.
    \end{cases}
  \end{equation*}
  Оставшиеся случаи разбираются аналогично.
\end{example}

>>>>

\engtitle{On a modification of the multistage bidding model with continuous bids and asymmetric information}

@@

\engabstract{%
  This paper is concerned with a modification of the multistage bidding model with continuous bids.
  Bidding takes place between two players for one unit of a risky asset.
  Player 1 knows the real price of the asset while Player 2 only knows probabilities of high and low prices of the asset.
  At each stage of the bidding players make real valued bids.
  The higher bid wins, and one unit of the risky asset is transacted to the winning player.
  The price of the transaction is equal to a convex combination of bids with a coefficient chosen in advance.
  Optimal strategies and the value of the $n$-stage game are found.
}

@@

  Пусть теперь $p_1 = h(\alpha), \; \alpha \in [0, 1]$.
  Введем обозначения
  \[
    \alpha^- = \inf \left\{ x \;|\; h(x) = h(\alpha) \right\}, \quad
    \alpha^+ = \sup \left\{ x \;|\; h(x) = h(\alpha) \right\}.
  \]
  Из \eqref{eq:W:lowerBound:parameterized} находим
  \begin{multline}\label{eq:g:+-}
    \G[p_1][h] = W_{2,n}(x + 1 - \alpha^- - \alpha^+) \enskip - \\
    - \int_0^{\alpha^-} \left(-\Co p_1 - \Dco h(u)\right) \di u
    - \int_{\alpha^+}^1 \left(\Dco p_1 + \Co h(u)\right) \di u.
  \end{multline}
  Поскольку $W_{2,n}(\cdot)$ -- дифференцируемая вогнутая функция, верно неравенство
  \begin{multline*}
    W_{2,n}(x + 1 - 2\alpha) \leqslant W_{2,n}(x + 1 - \alpha^- - \alpha^+) \enskip +\\
    + W_{2,n}'(x + 1 - \alpha^- - \alpha^+) \left( [ \alpha^+ - \alpha ] + [ \alpha^- - \alpha ] \right).
  \end{multline*}
  Из леммы \ref{lemma:hu:props} при $u_1 = (\alpha^- + \alpha^+)/2,\: u_2 = \alpha$ следует, что
  \[
  W_{2,n}'(x + 1 - \alpha^- - \alpha^+) = W_{2,n}'(x + 1 - 2\alpha) = h(\alpha).
  \]
  Так как $h(u)$ постоянна на $[\alpha^-, \alpha^+]$ и $h(\alpha) = p_1$ имеем
  \begin{multline*}
    W_{2,n}(x + 1 - \alpha^- - \alpha^+) \geqslant W_{2,n}(x + 1 - 2\alpha) - \\
    - \int_\alpha^{\alpha^+} \left( \Dco p_1 + \Co h(u) \right) \di u
    + \int_{\alpha^-}^\alpha \left( \Co p_1 + \Dco h(u) \right) \di u.
  \end{multline*}
  Используя оценку на $W_{2,n}(x + 1 - \alpha^- - \alpha^+)$ в \eqref{eq:g:+-}, получаем
  \begin{multline*}
    \G[p_1][h] \geqslant W_{2,n}(x + 1 - 2\alpha)
    - \int_\alpha^1 \biggl( \Dco h(\alpha) + \Co h(u) \biggr) \di u \; + \\
    + \int_0^\alpha \biggl( \Co h(\alpha) + \Dco h(u) \biggr) \di u = \G[h(\alpha)][h] = \Psi(h).
  \end{multline*}
  Таким образом, требуемое неравенство имеет место при любом значении $p_1 \in [0, 1]$.
\end{proof}

@@

\begin{example}
  Найдем оптимальные $f$ и $Q$ в игре $G_2(P)$.
  Из \eqref{eq:W1'} получаем
  \begin{equation*}
    W_1(x) = \begin{cases}
      x, &\; x \leqslant 1,\\
      1/4 (-1 + 2x - x^2), &\; -1 < x < 1,\\
      0, &\; x \geqslant 1.
    \end{cases}
  \end{equation*}
  Отсюда по формуле \eqref{eq:W':recursive} находим
  \begin{equation*}
    W'_2(x) = \frac{1}{2} \left( W_1(x+1) - W_1(x-1) \right) = \begin{cases}
      1, &\; x < -2,\\
      (4 - 4x - x^2)/8, &\; -2 \leqslant x < 0,\\
      (x - 2)^2/8, &\; 0 \leqslant x < 2,\\
      0, &\; x \geqslant 2.
    \end{cases}
  \end{equation*}
  \begin{figure}[h!]
    \begin{center}
      \includegraphics[height=6cm]{w2.eps}
      \fcaption{Функция $W_2'(x)$}
      \label{fig:w2}
    \end{center}
  \end{figure}
  Пусть $1/2 \leqslant P \leqslant 1$.
  Тогда (см. рис. \ref{fig:w2}) искомое $\lambda$ находится как решение уравнения $(4 - 4\lambda - \lambda^2)/8 = P$, т.е. $\lambda = -2 + 2\sqrt{2 - 2P}$.
  Отсюда получаем
  \begin{equation*}
    Q(u) = W'_1(\lambda + 1 - 2u) = \begin{cases}
      1 - \sqrt{2 - 2P} + u, &\; u < \sqrt{2 - 2P},\\
      1, &\; u \geqslant \sqrt{2 - 2P}.
    \end{cases}
  \end{equation*}
  Пусть $\Dco < \sqrt{2 - 2P}$.
  Тогда для $f$ имеет место следующая формула:
  \begin{equation*}
    f(u) = \begin{cases}
      1 - \sqrt{2 - 2P} + (2u + \Dco)/3, &\; u \leqslant \sqrt{2 - 2P},\\
      1 - \frac{(\sqrt{2 - 2P} - \Dco)^3}{3(u - \Dco)^2}, &\; u > \sqrt{2 - 2P}.
    \end{cases}
  \end{equation*}
  Оставшиеся случаи разбираются аналогично.
\end{example}
